Obtaining and assembling phylogenies

### 2017-02-17 Data/phylogenies.Rmd
just play a bit with this.

setwd("~/GitHub/Montreal_Workshop/Data")
int <- read.csv("interactions.csv", h = T)
#head(int)

@@

@@

# re-assign names to phylogeny
plant.phylo.int$tip.label<-names.compar$names.original
plot(plant.phylo.int,cex=0.6)

@@

# check if genus of these plants is in phylogeny
genus.insects<-sapply(strsplit(insects, "_"), "[", 1)
genus.phylo<-sapply(strsplit(all.phylo$tip.label, "_"), "[", 1)
genus.not.in.phylo<-unique(genus.insects[which(!genus.insects%in%genus.phylo)])
genus.not.in.phylo

>>>>

setwd("~/GitHub/Montreal_Workshop/Data")
#setwd("~/Documents/github/local/Montreal_Workshop/Data")
int <- read.csv("interactions.csv", h = T)
#head(int)

@@

IB: Halimium_conmutatum, is represented, can we use it as sister species?

@@

# re-assign names to phylogeny
plant.phylo.int$tip.label<-as.character(names.compar$names.original)
plot(plant.phylo.int,cex=0.6)

@@

# check if genus of these plants is in phylogeny
genus.insects<-sapply(strsplit(insects, "_"), "[", 1)
species.insects<-sapply(strsplit(insects, "_"), "[", 2)

genus.phylo<-sapply(strsplit(all.phylo$tip.label, "_"), "[", 1)
genus.not.in.phylo<-unique(genus.insects[which(!genus.insects%in%genus.phylo)])
genus.not.in.phylo

#check how many species per genus there are
temp <- colSums(table(data.frame(sp = species.insects, gen = genus.insects)))
summary(temp)
